### 2014-05-02 Response_to_R0_Reviews.tex

    This comment is greatly appreciated since the use of both B-mode and ARFI
    imaging for each segmentation was an important part of our methodology, and
    we (1) did not do enough to emphasize this point, and (2) confused matters
    by referring to `ARFI' exclusively in the results.  With respect to how the
    data were combined, we have added the following text to the manuscript
    (Section III(E.2)):

    \input{bmode_arfi_coregistered}

    We also agree that our exclusive use of `ARFI' for many of the tables,
    figures, manuscript title, and text was confusing, so we have updated all
    references to appropriate include B-mode when appropriate (not delineated
    here in the response due to the number of instances that were edited, but
    all manuscript changes are indicated in \textbf{bold} typeface).  The title
    of the manuscript has also been updated to reflect the importance of B-mode
    imaging in this process, and the abstract and conclusions have also been
    explicitly updated to include the fact that B-mode and ARFI imaging data
    were used in this study.

@@

    \item \textit{How many readers performed the B-Mode and ARFI segmentation
            per image? per entire study data set? Were the readers trained, and
            if so, how?  Did different readers segment the B-Mode and ARFI data
            sets?  Did the same radiologist who segmented the MRI images also
            segment the B-Mode and ARFI data?}

    All of the B-mode and ARFI images were segmented by two individuals (ZAM,
    TJG), and reviewed by two experienced ARFI imaging researchers (MLP and
    KRN).  There was no formal training in reading the ARFI images since this
    work is our first effort to analyze our ability to evaluate our accuracy in
    identifying structures in ARFI prostate images.  The same individuals
    segmented both the B-mode images (for the capsules) and ARFI images (for
    the central glands).  All of the MR images were segmented by an experienced
    radiology fellow (CK) and reviewed by an experienced prostate radiologist
    (RG).  We have added the following text to the manuscript to delineate the
    readers / image segmenters for each part of the study (Section III(E.1)):

@@

    \textbf{All MR image segmentations were ultimately reviewed by an
        experienced prostate radiologist (RTG).}

    And Section III(E.2):

    Sagittal B-mode and ARFI ultrasound image stacks were segmented in 3D
    Slicer \textbf{by two researchers (TJG \& ZAM)}\ldots

    \textbf{All B-mode and ARFI image segmentations were reviewed by two
        experienced ARFI imaging researcheres (MLP and KRN).}

@@

    We did mistakenly omit very relevant work that has been done with
    vibro-elastography and MR imaging in the prostate, and we have included
    this work in the manuscript's Introduction:

    \textbf{\input{intro_vibroelastography}}

\end{itemize}

\bibliographystyle{vancouver}
\bibliography{library_no_urls,slicer3d}

### 2014-05-02 coverletter.tex
updated coverletter for R1 submission

Re: \journal~Manuscript Submission
\vspace{0.25in}

@@

We thank you for taking the time and effort to review our manuscript, titled
{\it ``Acoustic Radiation Force Impulse (ARFI) Imaging Prostate Zonal Anatomy:
    Comparison with 3T T2-Weighted MR Imaging (T2WI)''}, for consideration to
be published in \journal.

>>>>

Re: UIX-14-0012 R1 Revision
\vspace{0.25in}

@@

We thank you for taking the time and effort to review our original manuscript,
and we have submitted a revision with a detailed, itemized response to the R0
comments.
